---
title: "Descriptive Statistics"
author: "Madan K C"
date: "04/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

I took the dataset of cars. It contains 
The dataset contains 50 observations and 2 variables, representing the speed and distance of cars.

```{r}
cars
View(cars)
```

  We can find minimum and maximum values using max() and min () functions.
```{r}
min(cars$dist)
max(cars$dist)
```


```{r}
min(cars$speed)
max(cars$speed)
```


```{r}
```
The **Range** also  gives minimun and maximum values.
```{r}
rnge<-range(cars$speed)
rnge
```
```{r}
rnge<-range(cars$dist)
rnge
```

```{r}
rnge[2]
```

We can find mean and median values using the functions mean() and median()
```{r}
mean(cars$speed)
median(cars$speed)
```

The **First Quartile**,**Third Quartile** and *IQR* have functions which are used below
```{r}
quantile(cars$speed, 0.25)
```
For the Third quartile we just need to change second parameter as **0.75**

```{r}
IQR(cars$speed)
```
 **Standard deviation and variance**

 
The standard deviation and the variance can be found using sd() and var() functions:

```{r}
sd(cars$speed)
var(cars$speed)
```
**Summary**
Summary will give summary for all the variables by a function called summary()

```{r}
summary(cars)
```

If we need the descriptive statistics by group we can apply a function by() 
```{r}
by(cars, cars$speed, summary)
```

```{r}
by(cars, cars$dist, summary)
```

Plotting the histogram for the speed of car

```{r}
hist(cars$speed, xlab="Speed", main="Histogram of Speed of Cars")
```

**BoxPlot**. 
  
Plotting Box Plots. They remove the outliers and ease the descriptive analysis.
  
```{r}
boxplot(cars$speed ~ cars$dist, xlab="distance", ylab="speed")
```
 
The freq() function produces frequency tables with frequencies, proportions, as well as missing data information.
```{r}
library(summarytools)
freq(cars$speed)
```